Preparación de datos

### 2022-10-24 production/prod_prep.Rmd
ajustes likertplot

# Chilean CENSUS data (2017)____________________________________________________
download.file(url = "https://github.com/jciturras/data-chile/raw/main/data/censo-2017/censo-2017.RData",
              destfile = here::here("input/data-original/censo17.Rdata"))

@@

# Attitudes toward inmigrants__________________________________________________
elsoc_long_2016_2021 <- 
elsoc_long_2016_2021 %>% 
  #create new variables
  mutate(in_simpat=r09,
         in_simili=r10,
         in_ansied=r11,
         in_valfam=r12_01,
         in_valami=r12_02,
         in_amsimb=r12_03,
         in_amreal=r12_04,
         in_acpier=r12_05,
         in_acadop=r12_06,
         in_amigcl=r12_07) %>% 
  sjlabelled::drop_labels(., drop.na = FALSE)

@@

df_study1 <- 
elsoc_long_2016_2021 %>% 
  filter(muestra == 1) %>% #keep original sample (vs refresh)
  select(idencuesta,ola,region,region_cod,comuna,comunacod=comuna_cod,
         muestra,
         cuestion_mig,
         starts_with("in_"),
         conviviality,
         identity,
         educ,educyear,
         # ing_pc,
         # quintil,
         quintil1,
         ess,
         # ess_inm,
         nation_t1,
         # know_inm,
         # know_inm_bi,
         # frien_inm_bi_t4,
         # frien_inm_bi_t1,
         know_inm_t1t4,
         # frien_inm,
         # frien_inm_bi,
         frien_inm_t1t4,
         pos_id,
         edad)

# Reshape long to wide
df_study1_wide <- df_study1 %>% 
  tidyr::pivot_wider(id_cols = c("idencuesta","muestra"),
                     names_from = "ola",
                     # names_prefix = c("educ","educyear","ing_pc","quintil","quintil1"),
                     values_from = names(select(df_study1,comuna,comunacod,cuestion_mig,in_simpat:edad))
                     )

@@

@@

# reshape from long to wide
pacman::p_load(datasets,data.table)
df_study1_long <- data.table::melt.data.table(data.table::setDT(df_study1_wide),
              id.vars = c("idencuesta","muestra"),
              variable.name = c("ola"),
              measure = patterns("^comuna_","^comunacod_","^cuestion_mig_",
                                 "^in_simpat_","^in_simili_","^in_ansied_","^in_valfam_",
                                 "^in_valami_","^in_amsimb_","^in_amreal_","^in_acpier_",
                                 "^in_acadop_","^in_amigcl_",
                                 "^conviviality","^identity",
                                 "^educ_","^educyear_","^quintil1_","^ess_","^nation_t1_",
                                 "^know_inm_t1t4_","^frien_inm_t1t4_","^pos_id_",
                                 "^edad_"
                                 ),
              value.name = c("comuna","comunacod","cuestion_mig",
                             "in_simpat","in_simili","in_ansied","in_valfam",
                             "in_valami","in_amsimb","in_amreal",
                             "in_acpier","in_acadop","in_amigcl",
                             "conviviality","identity",
                             "educ","educyear","quintil1","ess","nation_t1",
                             "know_inm_t1t4","frien_inm_t1t4","pos_id",
                             "edad"),
              na.rm = F,value.factor = TRUE
              )

@@

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

df_study_long_t5_comunas <- 
 dplyr::left_join(x = df_study1_long_t5,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

>>>>

# Chilean CENSUS data (2017)____________________________________________________
 options(timeout=100*100)
download.file(url = "https://github.com/jciturras/data-chile/raw/main/data/censo-2017/censo-2017.RData",
              destfile = here::here("input/data-original/censo17.Rdata"))

@@

# Attitudes toward inmigrants__________________________________________________
elsoc_long_2016_2021 <- 
elsoc_long_2016_2021 %>% 
  #create new variables
  mutate(in_simpat=r09,
         sexo=m0_sexo,
         in_simili=r10,
         in_ansied=r11,
         in_valfam=r12_01,
         in_valami=r12_02,
         in_amsimb=r12_03,
         in_amreal=r12_04,
         in_acpier=r12_05,
         in_acadop=r12_06,
         in_amigcl=r12_07) %>% 
  sjlabelled::drop_labels(., drop.na = FALSE)

@@

df_study1 <- 
elsoc_long_2016_2021 %>% 
  filter(muestra == 1) %>% #keep original sample (vs refresh)
  select(idencuesta,ola,region,region_cod,comuna,comunacod=comuna_cod,
         muestra,
         sexo,
         cuestion_mig,
         starts_with("in_"),
         conviviality,
         identity,
         educ,educyear,
         # ing_pc,
         # quintil,
         quintil1,
         ess,
         # ess_inm,
         nation_t1,
         # know_inm,
         # know_inm_bi,
         # frien_inm_bi_t4,
         # frien_inm_bi_t1,
         know_inm_t1t4,
         # frien_inm,
         # frien_inm_bi,
         frien_inm_t1t4,
         pos_id,
         edad)

# Reshape long to wide
df_study1_wide <- df_study1 %>% 
  tidyr::pivot_wider(id_cols = c("idencuesta","muestra"),
                     names_from = "ola",
                     # names_prefix = c("educ","educyear","ing_pc","quintil","quintil1"),
                     values_from = names(select(df_study1,comuna,comunacod,cuestion_mig,in_simpat:edad,sexo))
                     )

@@

df_study1_wide$sexo_2 <-df_study1_wide$sexo_1 #sex
df_study1_wide$sexo_3 <-df_study1_wide$sexo_1
df_study1_wide$sexo_4 <-df_study1_wide$sexo_1
df_study1_wide$sexo_5 <-df_study1_wide$sexo_1

@@

# reshape from long to wide
pacman::p_load(datasets,data.table)
df_study1_long <- data.table::melt.data.table(data.table::setDT(df_study1_wide),
              id.vars = c("idencuesta","muestra"),
              variable.name = c("ola"),
              measure = patterns("^comuna_","^comunacod_","^cuestion_mig_",
                                 "^in_simpat_","^in_simili_","^in_ansied_","^in_valfam_",
                                 "^in_valami_","^in_amsimb_","^in_amreal_","^in_acpier_",
                                 "^in_acadop_","^in_amigcl_",
                                 "^conviviality","^identity",
                                 "^educ_","^educyear_","^quintil1_","^ess_","^nation_t1_",
                                 "^know_inm_t1t4_","^frien_inm_t1t4_","^pos_id_",
                                 "^edad_","^sexo_"
                                 ),
              value.name = c("comuna","comunacod","cuestion_mig",
                             "in_simpat","in_simili","in_ansied","in_valfam",
                             "in_valami","in_amsimb","in_amreal",
                             "in_acpier","in_acadop","in_amigcl",
                             "conviviality","identity",
                             "educ","educyear","quintil1","ess","nation_t1",
                             "know_inm_t1t4","frien_inm_t1t4","pos_id",
                             "edad","sexo"),
              na.rm = F,value.factor = TRUE
              )

@@

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

df_study_long_t5_comunas <- 
 dplyr::left_join(x = df_study1_long_t5,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,sexo,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)
